### 2008-09-19 trunk/Papers/rmrs-08/motivation.tex
leidensdruck

In summary, \rmrs\ is a formalism for representing partial information
about semantic representations.  It generalizes \mrs\ in that it can
represent the output of a deep grammar in a way that is a notational
variant of \mrs; but in cases in which a deep grammar is not
available, it can be used to capture whatever partial semantic
information a shallower NLP tool was able to provide.  \rmrs\ is
designed to serve as a generic formalism for partial semantic
representations which abstracts over the details of different NLP
tools and allows us to represent, process, and compare information
from different tools in the same formalism.  In the long run, it could
also be a platform for incrementally enriching partial information
such as (\ref{ex:cat-pos}) in order to eventually approximate more
detailed representations such as (\ref{ex:cat-partial-parser}).

\todo{Leidensdruck!}

>>>>

In summary, \rmrs\ is a formalism for representing partial information
about semantic representations.  It generalizes \mrs\ in that it can
represent the output of a deep grammar in a way that is a notational
variant of \mrs; but in cases in which a deep grammar is not
available, it can be used to capture whatever partial semantic
information a shallower NLP tool was able to provide.  \rmrs\ is
designed to serve as a generic formalism for partial semantic
representations which abstracts over the details of different NLP
tools and allows us to represent, process, and compare information
from different tools in the same formalism, and in the long run
provide a platform for incrementally enriching partial information
such as (\ref{ex:cat-pos}) in order to eventually approximate more
detailed representations such as (\ref{ex:cat-partial-parser}).

However, although people have started using \rmrs\ in their
implemented systems, it is still relatively ad-hoc in that its formal
syntax is not consistent across different papers, and its formal
semantics is not defined; we don't know, formally, what an \rmrs\
\emph{means} in terms of semantic representations like
(\ref{ex:fat-cat-1}) and (\ref{ex:fat-cat-2}), and this hinders our
ability to come up with efficient algorithms for processing \rmrs. The
purpose of this paper is to lay the groundwork for fixing this problem.
